TCP Congestion Algorithms In Datacenters \\ \vspace{0.3cm} {\large LS Project}

### 2017-12-20 paper/paper.tex
Added BBR to do

TODO bbr turn on halfway through a test, does others' speed lessen?

>>>>

BBR appears to perform better in a congested network than the other tested protocols. In order to validate that BBR does not push away other TCP congestion algorithms a new testing method can be used. The data transfer with a TCP congestion algorithm is started and halfway the data transfer with BBR is started. This method shows whether a BBR data transfer has a large influence on the data transfer of other TCP congestion algorithms.
